---
title: "Coronavirus in the UK"
author: "Jia Xin Lin"
output: html_document
urlcolor: blue
bibliography: shiny_covid.bib
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r SetupImport, echo = FALSE, results = FALSE, message = FALSE, warning = FALSE}
library(shiny)
library(MASS)
library(rio)
library(readxl)
library(ggplot2)
library(scales)
library(shinythemes)
library(processx)
library(coronavirus)
library(tidyverse)
library(dplyr)
library(tidycovid19)
library(ggrepel)
library(gghighlight)
library(zoo)
library(lubridate)
library(splines)
Sys.setenv("LANGUAGE"="En")
Sys.setlocale("LC_ALL", "English")
CovidData <- download_merged_data(silent = TRUE, cached = TRUE)
CovidData <- CovidData %>%
  mutate(date = as.Date(parse_date_time(CovidData$date,orders=c("y","ym","ymd", "dmy"))))
UkData <- filter(CovidData, iso3c == "GBR")
firstdiff <- function(x) {
  shifted <- c(0,x[1:(length(x)-1)])
  result = x-shifted
  which_negative = which(result<0)
  result[which_negative] = NA
  return(result)
}
UkData <- UkData %>%
  mutate(day_date = yday(date),
         daily_confirmed = firstdiff(confirmed),
         daily_recovered = firstdiff(recovered),
         daily_deaths = firstdiff(deaths),
         daily_vaccine = firstdiff(total_vaccinations),
         ave_daily_confirmed = rollmean(daily_confirmed, 7, na.pad=TRUE, align="right"),
         ave_daily_recovered = rollmean(daily_recovered, 7, na.pad=TRUE, align="right"),
         ave_daily_deaths = rollmean(daily_deaths, 7, na.pad=TRUE, align="right"),
         ave_daily_vaccine = rollmean(daily_vaccine, 7, na.pad=TRUE, align="right"),
         ave_confirmed = rollmean(confirmed, 7, na.pad=TRUE, align="right"),
         ave_recovered = rollmean(recovered, 7, na.pad=TRUE, align="right"),
         ave_deaths = rollmean(deaths, 7, na.pad=TRUE, align="right"),
         ave_vaccine = rollmean(total_vaccinations, 7, na.pad=TRUE, align="right"))
```

The coronavirus is still spreading around the world today, which affects more than 200 countries. This report aims to examine the COVID-19 in the UK. The graphs and tables in this report uses data from the `tidycovid19` package, which collects data from Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository,  Google COVID-19 Community Mobility Reports and many other reliable resources. More details can be found on this [website](https://joachim-gassen.github.io/tidycovid19/).


## Confirmed, recovered and dead cases

```{r Page1, echo=FALSE, message = FALSE, warning = FALSE}
mainPanel(width = 15,
      selectInput("class", "Plot:",
                   c("Cases", "Recovered", "Deaths", "Vaccination")
      ),
      conditionalPanel("input.class === 'Cases'",
                    h4("Daily and Cumulative Cases in the UK"),
                    p("This plot shows the exact number of daily and cumulative cases with the 7-day moving average line, which shows the trend." )
      ),
      conditionalPanel("input.class === 'Recovered'",
                     h4("Daily and Cumulative Testing in the UK"),
                     p("This plot shows the exact number of daily and cumulative testing with the 7-day moving average line, which shows the trend.")
      ),
      conditionalPanel("input.class === 'Deaths'",
                     h4("Daily and Cumulative deaths"),
                     p("This bar chart gives an overall idea of the daily and cumulative number of deaths with the 7-day moving average line, which shows the trend.")
      ),
      conditionalPanel("input.class === 'Vaccination'",
                     h4("Daily and Cumulative vaccinations"),
                     p("This bar chart gives an overall idea of the daily and cumulative number of vaccinations with the 7-day moving average line, which shows the trend.")
     ),
      tabsetPanel(
        tabPanel("Daily", plotOutput("plot1", height = 500), textOutput("analysis1")), 
        tabPanel("Cumulative", plotOutput("plot2", height = 500), textOutput("analysis2"))
     )
 )
```

```{r Plots1, echo = FALSE, results = FALSE, message = FALSE, warning = FALSE}
Sys.setlocale("LC_ALL", "English")
CasePlotDa <- UkData %>%
        filter(!is.na(daily_confirmed), !is.na(ave_daily_confirmed)) %>%
        ggplot(aes(x = date)) + 
        geom_bar(aes(y = daily_confirmed, fill = "Number of cases"),stat = "identity") +
        xlab("Date") + ylab("Daily Cases") +
        ggtitle("Cases in UK (2020/21)") +
        theme(plot.title = element_text(lineheight=.8, face="bold"))  +
        geom_line(aes(y=ave_daily_confirmed, colour = "Cases (7-day average)"), size = 1.2, alpha = 0.85) +
        scale_fill_manual(name = "", values = c("Number of cases" = "orange2")) +
        scale_colour_manual(name = "", values = c("Cases (7-day average)" = "sienna")) +
        scale_x_date(date_breaks = "2 month",
                     date_minor_breaks = "1 month", date_labels = "%b-%y")

RePlotDa <- UkData %>%
        filter(!is.na(daily_recovered), !is.na(ave_daily_recovered)) %>%
        ggplot(aes(x = date)) + 
        geom_bar(aes(y = daily_recovered, fill = "Numbere of Recovery"), stat = "identity" ) +
        xlab("Date") + ylab("Daily Recovery") +
        ggtitle("Recovery in UK (2020/21)") +
        geom_line(aes(y=ave_daily_recovered, colour = "Recovery (7-day average)"), size = 1.2, alpha = 0.7) +
        theme(plot.title = element_text(lineheight=.8, face="bold")) +
        theme(axis.text.y = element_text(size=10)) +
        scale_fill_manual(name = "", values = c("Numbere of Recovery" = "steelblue3"))+
        scale_colour_manual(name = "", values = c("Recovery (7-day average)" = "navy")) +
        scale_x_date(date_breaks = "2 month",
                     date_minor_breaks = "1 month",
                     date_labels = "%b")  +
        scale_y_continuous(labels = comma_format(big.mark = "." , 
                                                 decimal.mark = ","))

DeathPlotDa <- UkData %>%
        filter(!is.na(daily_deaths), !is.na(ave_daily_deaths)) %>%
        ggplot(aes(x = date))+
        geom_bar(aes(y = daily_deaths, fill = "Deaths"),stat = "identity", position = "stack") +
        geom_line(aes(y=ave_daily_deaths, colour = "Deaths (7-day average)"), size = 1.2, alpha = 0.9) +
        scale_x_date(date_breaks = "2 month",
                     date_minor_breaks = "1 month",
                     date_labels = "%b")  +
        xlab("Date")+ylab("Daily Deaths") +
        ggtitle("Deaths within 28 days of positive test by date of death (UK, 2020/21)") +
        theme(plot.title = element_text(lineheight=.8, face="bold"))+
        scale_fill_manual(name = "", values = c("Deaths" = "firebrick3"))+
        scale_colour_manual(name = "", values = c("Deaths (7-day average)" = "coral4"))

VacPlotDa <- UkData %>%
        filter(!is.na(daily_vaccine), !is.na(ave_daily_vaccine)) %>%
        ggplot(aes(x = date))+
        geom_bar(aes(y = daily_vaccine, fill = "Number of Vaccinations"), stat = "identity", position = "stack") +
        geom_line(aes(y=ave_daily_vaccine, colour = "Vaccinations (7-day average)"), size = 1.2, alpha = 0.7) +
        scale_x_date(date_breaks = "2 month",
                     date_minor_breaks = "1 month",
                     date_labels = "%b")  +
        xlab("Date")+ylab("Daily numbers of vaccinations") +
        scale_fill_manual(name = "", values = c("Number of Vaccinations" = "steelblue"))+
        scale_colour_manual(name = "", values = c("Vaccinations (7-day average)" = "navy"))+
        ggtitle("Vaccinations given against to the COVID-19 (UK, 2020/21)") +
        theme(plot.title = element_text(lineheight=.8, face="bold"))
```

```{r Plot2, echo = FALSE, results = FALSE, message = FALSE, warning = FALSE}
CasePlotCum <- UkData %>%
          filter(!is.na(confirmed), !is.na(ave_confirmed)) %>%
          ggplot(aes(x = date)) + 
          geom_bar(aes(y = confirmed, fill = "Number of cases"),stat = "identity") +
          xlab("Date") + ylab("Cumulative Cases") +
          ggtitle("Cases in UK (2020/21)") +
          theme(plot.title = element_text(lineheight=.8, face="bold"))  +
          geom_line(aes(y=ave_confirmed, colour = "Cases (7-day average)"), size = 1.2, alpha = 0.85) +
          scale_fill_manual(name = "", values = c("Number of cases" = "orange2")) +
          scale_colour_manual(name = "", values = c("Cases (7-day average)" = "sienna"))+
          scale_x_date(date_breaks = "2 month",
                     date_minor_breaks = "1 month", date_labels = "%b-%y")

RePlotCum <- UkData %>%
          filter(!is.na(recovered), !is.na(ave_recovered)) %>%
          ggplot(aes(x = date)) + 
          geom_bar(aes(y = recovered, fill = "Numbere of Recovery"), stat = "identity" ) +
          xlab("Date") + ylab("Cumulative Recovery") +
          ggtitle("Recovery in UK (2021)") +
          geom_line(aes(y=ave_recovered, colour = "Recovery (7-day average)"), size = 1.2, alpha = 0.7) +
          theme(plot.title = element_text(lineheight=.8, face="bold")) +
          theme(axis.text.y = element_text(size=10)) +
          scale_fill_manual(name = "", values = c("Numbere of Recovery" = "steelblue3"))+
          scale_colour_manual(name = "", values = c("Recovery (7-day average)" = "navy")) +
          scale_x_date(date_breaks = "2 month",
                       date_minor_breaks = "1 month",
                       date_labels = "%b")  +
          scale_y_continuous(labels = comma_format(big.mark = "." , 
                                                   decimal.mark = ","))

DeathPlotCum <- UkData %>%
            filter(!is.na(deaths), !is.na(ave_deaths)) %>%
            ggplot(aes(x = date))+
            geom_bar(aes(y = deaths ,fill = "Deaths"),stat = "identity", position = "stack") +
            geom_line(aes(y=ave_deaths, colour = "Deaths (7-day average)"), size = 1.2, alpha = 0.9) +
            scale_x_date(date_breaks = "2 month",
                         date_minor_breaks = "1 month",
                         date_labels = "%b")  +
            xlab("Date")+ylab("Cumulative Deaths") +
            ggtitle("Deaths within 28 days of positive test by date of death (UK, 2020/21)") +
            theme(plot.title = element_text(lineheight=.8, face="bold"))+
            scale_fill_manual(name = "", values = c("Deaths" = "firebrick3"))+
            scale_colour_manual(name = "", values = c("Deaths (7-day average)" = "darkred"))+
            scale_y_continuous(labels = comma_format(big.mark = "." , 
                                                     decimal.mark = ","))

VacPlotCum <- UkData %>%
            filter(!is.na(total_vaccinations), !is.na(ave_daily_vaccine)) %>%
            ggplot(aes(x = date))+
            geom_bar(aes(y = total_vaccinations, fill = "Number of Vaccinations"), stat = "identity", position = "stack") +
            geom_line(aes(y=ave_vaccine, colour = "Vaccinations (7-day average)"), size = 1.2, alpha = 0.7) +
            scale_x_date(date_breaks = "2 month",
                         date_minor_breaks = "1 month",
                         date_labels = "%b")  +
            xlab("Date")+ylab("Cumulative numbers of vaccinations") +
            scale_fill_manual(name = "", values = c("Number of Vaccinations" = "steelblue"))+
            scale_colour_manual(name = "", values = c("Vaccinations (7-day average)" = "navy"))+
            ggtitle("Vaccinations given against to the COVID-19 (UK, 2020/21)") +
            theme(plot.title = element_text(lineheight=.8, face="bold"))+
            scale_y_continuous(labels = comma_format(big.mark = "." , 
                                                     decimal.mark = ","))
```

```{r Output1, echo = FALSE}
output$plot1 <- renderPlot({
    if (input$class == "Cases") {
      print(CasePlotDa)
    } else if (input$class == "Recovered") {
      print(RePlotDa)
    } else if (input$class == "Vaccination"){
      print(VacPlotDa)
    } else if (input$class == "Deaths"){
      print(DeathPlotDa)
    }
  })

output$plot2 <- renderPlot({
    if (input$class == "Cases") {
      print(CasePlotCum)
    } else if (input$class == "Recovered") {
      print(RePlotCum)
    } else if (input$class == "Vaccination"){
      print(VacPlotCum)
    } else if (input$class == "Deaths"){
      print(DeathPlotCum)
    }
  })

output$analysis1 <- renderText({
  if (input$class == "Cases") {
      "From the plot, we can see the three major waves as a whole. The first wave is from February to July 2020, the second is from October 2020 to April 2021, and the third is still ongoing from June 2021."
    } else if (input$class == "Recovered") {
      ""
    } else if (input$class == "Vaccination"){
      ""
    } else if (input$class == "Deaths"){
      ""
    }  
})

output$analysis2 <- renderText({
  if (input$class == "Cases") {
      ""
    } else if (input$class == "Recovered") {
      ""
    } else if (input$class == "Vaccination"){
      ""
    } else if (input$class == "Deaths"){
      ""
    }  
})
```

## Regression models for the Coronavirus data in the UK

We are going to look at the confirmed cases, which is count data. Hence, by *Regression Models for Count Data in R* [@RegModel2007], it is recommended to use Poisson, geometric and negative-binomial regression models. In this report, we will try to fit our data with Poisson and negative-binomial models.

Before we start, there are some concepts and notations we need to clarify:

- Effective reproduction number ($R$): The number of secondary infections expected from a typical primary case in the population through which the disease is spreading, in this case, the COVID-19.
  - if $R$ > 1: the number of infections will increase exponentially in time
  - if $R$ < 1: the number of infections will decrease exponentially in time
- Serial interval ($T_{C}$): Mean of the generation interval. In this case, our $T_{C}$ = 4 [@SerialInterval2020].
- $I(t)$: The number of infected individual at time $t$, which is given by
  $$I(t) = I(0)R^{\frac{t}{T_{C}}}$$ where $I(0)$ is the initial infected individuals number.
Since $R$ is usually unknown, hence we can rewrite the above equation as:
  $$I(t) = I(0)exp(rt)$$ and then $R = exp(rT_{C})$ with $r$ being a coefficient, we can obtain from the model summary. In addition, the number of infected individuals doubles after $time = log(2)/r$.

```{r Page2, echo=FALSE, message = FALSE, warning = FALSE}
mainPanel(width = 15,
      selectInput("class2", "Waves:",
                   c("First", "Second", "Third")
      ),
      conditionalPanel("input.class2 === 'First'",
                    h4("First Wave in the UK (February - July 2020)"),
                    p("These plots show how Poisson and negative-binomial models fits our first wave data.")
      ),
      conditionalPanel("input.class2 === 'Second'",
                     h4("Second Wave in the UK (October 2020 - April 2021)"),
                     p("These plots show how Poisson and negative-binomial models fits our sencond wave data.")
      ),
      conditionalPanel("input.class2 === 'Third'",
                     h4("Third Wave in the UK (June 2021 - )"),
                     p("These plots show how Poisson and negative-binomial models fits our third wave data.")
      ),
      tabsetPanel(
        tabPanel("Poisson", plotOutput("plot3", height = 500), textOutput("analysis3")), 
        tabPanel("Negative-Binomial", plotOutput("plot4", height = 500), textOutput("analysis4"))
     )
 )
```

```{r Poissonfit, echo=FALSE, message = FALSE, warning = FALSE}
UKCasesData <- {UkData %>%
    dplyr::select(date, day_date, daily_confirmed)}

FirstWaveUkData <- {UKCasesData %>% 
    filter( (date > as.Date("2020-02-01")) & (date < as.Date("2020-07-31")) )} %>%
    filter(!is.na(daily_confirmed), !is.na(day_date))
Poisson_fit1 <- glm(daily_confirmed ~ 1 + day_date + I(day_date^2) + I(log(day_date)), family = poisson, data = FirstWaveUkData)
FirstWaveUkData$pred_poisson = predict(Poisson_fit1)
PoissonCases1 <- {FirstWaveUkData %>% ggplot(aes(x = day_date, y = daily_confirmed))} +
  xlab("Days") +
  ylab("Number of new confirmed daily cases") +
  geom_point() +
  geom_line(aes(y = exp(pred_poisson)), size = 1) +
  ggtitle("Regression plot for the number of new confirmed daily cases fitted with Poisson model",
                       subtitle = "UK, February - July, 2020")

SecondWaveUkData <- {UKCasesData %>% 
    filter( (date > as.Date("2020-10-01")) & (date < as.Date("2021-04-30")) )} %>%
    filter(!is.na(daily_confirmed), !is.na(day_date))
Poisson_fit2 <- glm(daily_confirmed ~ 1 + day_date + I(day_date^2) + I(log(day_date)), family = poisson, data = SecondWaveUkData)
SecondWaveUkData$pred_poisson = predict(Poisson_fit2)
PoissonCases2 <- {SecondWaveUkData %>% ggplot(aes(x = day_date, y = daily_confirmed))} +
  xlab("Days") +
  ylab("Number of new confirmed daily cases") +
  geom_point() +
  geom_line(aes(y = exp(pred_poisson)), size = 1) +
  ggtitle("Regression plot for the number of new confirmed daily cases fitted with Poisson model",
                       subtitle = "UK, October 2020 - April 2021")

ThirdWaveUkData <- {UKCasesData %>% 
    filter( date > as.Date("2021-06-01"))} %>%
    filter(!is.na(daily_confirmed), !is.na(day_date))
Poisson_fit3 <- glm(daily_confirmed ~ 1 + day_date + I(day_date^2) + I(log(day_date)), family = poisson, data = ThirdWaveUkData)
ThirdWaveUkData$pred_poisson = predict(Poisson_fit3)
PoissonCases3 <- {ThirdWaveUkData %>% ggplot(aes(x = day_date, y = daily_confirmed))} +
  xlab("Days") +
  ylab("Number of new confirmed daily cases") +
  geom_point() +
  geom_line(aes(y = exp(pred_poisson)), size = 1) +
  ggtitle("Regression plot for the number of new confirmed daily cases fitted with Poisson model",
          subtitle = "UK, June 2021 - ")
```

```{r NBinomialfit, echo=FALSE, message = FALSE, warning = FALSE}
NB_fit1 <- glm.nb(daily_confirmed ~ 1 + (day_date + I(day_date^2) + I(log(day_date)))^2, data = FirstWaveUkData)
FirstWaveUkData$pred_nbinomial = predict(NB_fit1)
NBCases1 <- {FirstWaveUkData %>% ggplot(aes(x = day_date, y = daily_confirmed))} +
  xlab("Days") +
  ylab("Number of new confirmed daily cases") +
  geom_point() +
  geom_line(aes(y = exp(pred_nbinomial)), size = 1) +
  ggtitle("Regression plot for the number of new confirmed daily cases fitted with negative-binomial model",
                       subtitle = "UK, February - July, 2020")

NB_fit2 <- glm.nb(daily_confirmed ~ 1 + day_date + I(day_date^2) + I(log(day_date)), data = SecondWaveUkData)
SecondWaveUkData$pred_nbinomial = predict(NB_fit2)
NBCases2 <- {SecondWaveUkData %>% ggplot(aes(x = day_date, y = daily_confirmed))} +
  xlab("Days") +
  ylab("Number of new confirmed daily cases") +
  geom_point() +
  geom_line(aes(y = exp(pred_nbinomial)), size = 1) +
  ggtitle("Regression plot for the number of new confirmed daily cases fitted with negative-binomial model",
                       subtitle = "UK, October 2020 - April 2021")

NB_fit3 <- glm.nb(daily_confirmed ~ 1 + day_date + I(day_date^2) + I(log(day_date)), data = ThirdWaveUkData)
ThirdWaveUkData$pred_nbinomial = predict(NB_fit3)
NBCases3 <- {ThirdWaveUkData %>% ggplot(aes(x = day_date, y = daily_confirmed))} +
  xlab("Days") +
  ylab("Number of new confirmed daily cases") +
  geom_point() +
  geom_line(aes(y = exp(pred_nbinomial)), size = 1) +
  ggtitle("Regression plot for the number of new confirmed daily cases fitted with negative-binomial model",
                       subtitle = "UK, June 2021 - ")
```

```{r Output2, echo = FALSE, message = FALSE, warning = FALSE}
output$plot3 <- renderPlot({
    if (input$class2 == "First") {
      print(PoissonCases1)
    } else if (input$class2 == "Second") {
      print(PoissonCases2)
    } else if (input$class2 == "Third"){
      print(PoissonCases3)
    }
  })

output$plot4 <- renderPlot({
    if (input$class2 == "First") {
      print(NBCases1)
    } else if (input$class2 == "Second") {
      print(NBCases2)
    } else if (input$class2 == "Third"){
      print(NBCases3)
    }
  })

output$analysis3 <- renderText({
  if (input$class2 == "First") {
      ""
    } else if (input$class2 == "Second") {
      ""
    } else if (input$class2 == "Third"){
      ""
    }
  })

output$analysis4 <- renderText({
  if (input$class2 == "First") {
      ""
    } else if (input$class2 == "Second") {
      ""
    } else if (input$class2 == "Third"){
      ""
    }
  })
```

## Impact of lockdown on behavioural indicators

We are now going to look at how did people's behaviour change during lockdowns. We are going to use data from [Google Community Mobility Reports](https://www.google.com/covid19/mobility/index.html?hl=en), which collects Location History from android mobile devices to chart movement trends across different categories of places.

```{r Page3, echo=FALSE, message = FALSE, warning = FALSE}
mainPanel(width = 15,
      selectInput("class3", "Plot:",
                   c("Residential", "Workplaces", "Transit Stations", "Grocery/Pharmacy")
      ),
      conditionalPanel("input.class3 === 'Residential'",
                    h4("Percentage Change in Frequency that People Visit Residential Places"),
                    p("The plot shows how did the measurement of activity in the residential places change compared to the baseline period (UK, Jan 3 - Feb 6, 2020) expressed as a percentage." )
      ),
      conditionalPanel("input.class3 === 'Workplaces'",
                     h4("Percentage Change in Frequency that People Visit Workplaces"),
                     p("The plot shows how did the measurement of activity in the workplaces change compared to the baseline period (UK, Jan 3 - Feb 6, 2020) expressed as a percentage.")
      ),
      conditionalPanel("input.class3 === 'Transit Stations'",
                     h4("Percentage Change in Frequency that People Visit Residential Places"),
                     p("This bar chart gives an overall idea of the percentage change in frequency that people visit transit stations.")
      ),
      conditionalPanel("input.class3 === 'Grocery/Pharmacy'",
                     h4("Percentage Change in Frequency that People Visit Grocery or Pharmacy"),
                     p("This bar chart gives an overall idea of the percentage change in frequency that people visit grocery or pharmacy.")
     ),
        plotOutput("plot5", height = 500),
        textOutput("analysis5")
 )
```

```{r Plot5, echo = FALSE, message = FALSE, warning = FALSE}
UKBehaveData <- {UkData %>% 
    select(date, confirmed, daily_confirmed, gcmr_residential, gcmr_workplaces, gcmr_transit_stations, gcmr_grocery_pharmacy) }
UKBehaveData <- UKBehaveData %>%
  mutate(Weekdays = weekdays(date))

PlotResidentialDate <- {UKBehaveData %>% 
    ggplot(aes(x = date, y = gcmr_residential, color = Weekdays))} + 
    geom_point() + 
    xlab("Date") +
    ylab("Activity in residences (% change)") +
    ggtitle("Percentage change of activity in residences from baseline (UK)", 
                subtitle = "Drawn from Google Community Mobility Reports") +
    scale_x_date(date_breaks = "months", date_labels = "%b-%y")

PlotWorkplacesDate <- {UKBehaveData %>% 
    ggplot(aes(x = date, y = gcmr_workplaces, color = Weekdays))} + 
    geom_point() + 
    xlab("Date") +
    ylab("Activity in workplaces (% change)") +
    ggtitle("Percentage change of activity in workplaces from baseline (UK)", 
                subtitle = "Drawn from Google Community Mobility Reports") +
    scale_x_date(date_breaks = "months", date_labels = "%b-%y")

PlotTransitDate <- {UKBehaveData %>% 
    ggplot(aes(x = date, y = gcmr_transit_stations, color = Weekdays))} + 
    geom_point() + 
    xlab("Date") +
    ylab("Activity in transit stations (% change)") +
    ggtitle("Percentage change of activity in transit stations from baseline (UK)", 
                subtitle = "Drawn from Google Community Mobility Reports") +
    scale_x_date(date_breaks = "months", date_labels = "%b-%y")

PlotGroceryDate <- {UKBehaveData %>% 
    ggplot(aes(x = date, y = gcmr_grocery_pharmacy, color = Weekdays))} + 
    geom_point() + 
    xlab("Date") +
    ylab("Activity in groceries or pharmacies (% change)") +
    ggtitle("Percentage change of activity in groceries or pharmacies from baseline (UK)", 
                subtitle = "Drawn from Google Community Mobility Reports") +
    scale_x_date(date_breaks = "months", date_labels = "%b-%y")
```

```{r Output3, echo = FALSE}
output$plot5 <- renderPlot({
    if (input$class3 == "Residential") {
      print(PlotResidentialDate)
    } else if (input$class3 == "Workplaces") {
      print(PlotWorkplacesDate)
    } else if (input$class3 == "Transit Stations"){
      print(PlotTransitDate)
    } else if (input$class3 == "Grocery/Pharmacy"){
      print(PlotGroceryDate)
    }
  })

output$analysis5 <- renderText({
    if (input$class3 == "Residential") {
      ""
    } else if (input$class3 == "Workplaces") {
      ""
    } else if (input$class3 == "Transit Stations"){
      ""
    } else if (input$class3 == "Grocery/Pharmacy"){
      ""
    }
  })
```

## References
::: {#refs}
:::